Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
re-cite Hsu 2003

Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that SVMs should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges. \ja{Again, it would be really good if we could cite something for this.}
This operation may also help making the dataset linearly separable in feature space. \ja{Why?}
To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mu[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mu[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the sample mean of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mu[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
is the sample standard deviation.

>>>>

Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that SVMs should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges \cite{Hsu2003}.

To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mu[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mu[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the sample mean of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mu[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
is the sample standard deviation.
